Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-09 ms.tex
enum and figure
the issues column is back.
minor

The source term in equation (\ref{eq:drhodt}),
\begin{align}
  q=\frac{\eta \rhostar}{\th},
\label{eq:q}
\end{align}
represents mass input from stellar winds, which we parameterize in
terms of the fraction $\eta$ of the stellar density $\rhostar$ being
recycled into gas on the Hubble time $\th = 1.4 \times 10^{10}$
yr.  To good approximation $\eta\simeq 0.02 (\tau_{\star}/t_h)^{-1.3}$ at time $\tau_{\star}$ following an impulsive star burst (e.g., \citealt{Ciotti+91})\footnote{\citet{Ciotti+91} give the mass return rate from evolved stars as a function of B-band luminosity instead of volumetrically, but our expressions are equivalent.}, although $\eta$ is significantly higher for continuous star formation histories (Fig.~\ref{fig:eta}).

@@

Our analytic derviations neglect the effects of heat conduction, an assumption we now check.  The ratio of the magnitude of the conductive heating rate (eq.~[\ref{eq:qdotcond}]) to the external heating rate at the stagnation radius is given by
\begin{align}
  \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
w}^{2}/2}\right|_{r_{\rm s}} &\sim \frac{2t_{\rm h}\kappa_0
T|_{r_{\rm s}}^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}|_{r_{\rm s}}
\tilde{v}_{w}^{2}}
 \left(\frac{1}{1+\frac{\kappa_0 T^{7/2}|_{r_{\rm s}}}{5 \rs
    \phi \rho c_s^3}}\right)
\nonumber \\ &\sim {\rm min}
  \begin{cases}
  20 \eta_{0.02}^{-1}
M_{\bullet,8}^{-0.8} v_{500}^{6.8} &  \text{unsaturated (core)}\\
 20 \eta_{0.02}^{-1}
M_{\bullet,8}^{-0.5} v_{500}^{5.4} &  \text{unsaturated (cusp)}\\
  2 \phi & \text{saturated},
  \end{cases}
 \label{eq:conduction}
\end{align}
where the second equality makes use of equations (\ref{eq:Tanalytic}),
(\ref{eq:stag_simple}), and we have approximated $\nabla^{2} \sim
1/r_{\rm s}^{2}$, $\nabla \sim 1/r_{\rm s}$.  We have approximated the
stellar density profile as (eq.~[\ref{eq:rhostar}])
\begin{eqnarray}
  \rho_{\star}|_{r_{\rm s}} &\simeq& \frac{M_{\bullet}(2-\Gamma)}{4\pi r_{\rm soi}^{3}}\left(\frac{r_{\rm s}}{r_{\rm soi}}\right)^{-1-\Gamma} \nonumber \\
 &\approx& \begin{cases}
    6.1 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
    & \text{core} \\
    2.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
    \,{\rm g\,cm^{-3}}  & \text{cusp}, 
  \end{cases}
  \label{eq:rhostarrs}
\end{eqnarray}
where the stagnation radius is assume to reside well inside the Nuker
break radius and for clarity we have not distinguished between cusp and core galaxies.  Equation (\ref{eq:conduction}) shows that even in the
case of saturated conduction, the neglect of heat conduction results
in at most an order unity correction for expected values of the
saturation parameter $\phi < 0.1$, justifying its neglect in our
analysis.  Numerical experiments including conductivity confirm this
($\S\ref{sec:numerical}$).

@@

\citet{EmsellemCappellari+:2007a} use two-dimensional kinematic data to measure the ratio of ordered to random motion in a sample of early type galaxies, which they quantify at each galactic radius $R$ by the parameter
  \begin{align}
    \lambda_R \equiv \frac{\langle r|V|\rangle}{\langle R\sqrt{V^2+\sigma^2}\rangle} \underset{R \ll r_{\rm soi}}\sim \frac{V_{\phi}}{\sigma},
  \end{align}
where $\sigma$ is the velocity dispersion and the brackets indicate a luminosity-weighted average.  The circularization radius of the accretion flow can be written in terms of $\lambda_R$ as
\begin{equation}
\frac{r_{\rm circ}}{r_{s}} \approx \frac{r_{s}}{r_{\rm soi}}\lambda_{R}^{2} \lesssim \lambda_{R}^{2},
\label{eq:rcirc}
\end{equation}
where we have used the definition $r_{\rm soi} \equiv GM_{\bullet}/\sigma^{2}$ and in the second inequality have assumed that $r_{\rm s} \lesssim r_{\rm soi}$, a condition which is satisfied for the thermally-stable solutions of interest.

\citet{EmsellemCappellari+:2007a} (their Fig.~2) find that $\lambda_R$ is generally $< 0.1$ on radial scales $<$ 10 per cent of the galaxy half-light radius and that $\lambda_R$ is with $R$ interior to this point.  From equation (\ref{eq:rcirc}) we thus conclude that $r_{\rm circ} \lesssim 0.01r_{s}$, i.e.~that gas will circularize well inside the inner sonic point of the flow (typically located at $\sim 0.1r_{\rm s}$; Fig.~\ref{fig:profiles}).  Angular momentum should only become dynamically important for thermally stable flows in a region that is causally disconnected from the outer part of the flow where the mass accretion rate is determined.

@@

  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $\Gamma$ &  $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.2}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$}  \\

@@

...$^{\dagger}$ & ... & 0.8 & 100 & 0.29 & $ 1.5 \times 10^{ -4 }$ & 70 \\

@@

$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 9.9 \times 10^{ -2 }$ & $ 8.2 \times 10^{ -6 }$ & 99 \\

@@

\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in
Eddington units, normalized to a stellar mass input parameter $\eta =
0.2$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
stagnation radius.  Thermally unstable solutions are shown in bold
text.  $\dagger$Calculated with full radiative cooling included, assuming mass loss parameter $\eta = $? 
\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

Realistic variations (``burstiness") in the star formation history
will often result in lower heating rates.  Figure \ref{NickPlot2}
shows the heating rate as a function of average black hole mass for
non-fiducial cases in which the current ($z = 0$) star formation is
suppressed by a factor $\zeta$ from its average $z = 0$ value, for a
characteristic timescale $t_{\rm scale}$ (for details, see Appendix
\ref{app:windheat}).  For $t_{\rm scale} \lesssim 10^{7}$ yr, we see
that $v_{\rm w}^{\star}$ is reduced by at most a factor of $\approx 2$
from its average value, even for huge drops in the star formation rate
($\zeta \sim 10^{-3}$).  However, burstiness in the star formation
history over longer timescales can suppress heating more
significantly.  When $t_{\rm scale} \gtrsim 10^8~{\rm yr}$, $v_{\rm
  w}^\star$ becomes very sensitive to $\zeta$: at $\zeta=0.1$, $v_{\rm
  w}^\star \approx 500~{\rm km~s}^{-1}$ in most galaxies, but for
smaller $\zeta$, $v_{\rm w}^\star \approx 200~{\rm km~s}^{-1}$ (an
exception to this is in galactic nuclei with $M_\bullet \gtrsim
5\times 10^8~M_\odot$, where heating is stabilized by SN Ia).  Our use
of average cosmic star formation histories is appropriate provided
local variations are either on short timescales ($t_{\rm scale}
\lesssim 10^7~{\rm yr}$), or limited in magnitude ($\zeta \gtrsim
0.1$).  If both of these conditions are violated, then the effective
heating rates for all but the most massive galaxies (where Ia
explosions dominate) will fall by a factor $\approx 5$ from our
fiducial volumetric averages, taken from \citet{MosterNaab+:2013a}.

@@

Figure \ref{fig:bh_growth} (top panel) shows that across all black
hole masses, Compton heating alone cannot prevent thermal
instabilities from developing in a steady-state accretion flow
($\dot{M}_{\rm C} > \dot{M}_{\rm TI}$).  Thus, if the stellar
population is sufficiently old (or the star formation sufficiently
intermittent) then nuclear gas could undergo cyclic oscillations of
thermal instability and high accretion rates, followed by quiescent
periods once gas has been consumed and/or AGN feedback becomes
effective.  Such cycles are proposed to occur on large scales and long
timescales in elliptical galaxies (\citealt{Ciotti+10}), an idea
supported, e.g. , by GALEX observations showing that a small fraction
of early-type galaxies in the local universe have undergone recent ($<
1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).  If such
cyclic behavior also occurs on small, parsec scales (e.g.) then the
large scatter in the accretion rates and hence X-ray luminosities
shown in Fig \ref{fig:Miller} could also be understood by the wide
range of gas masses experienced over the course of a cyclic episode
between instabilities and periodic nuclear outbursts
(e.g.~\citealt{Ciotti+10}).  In support of this possibility, we find
that core galaxies are more likely to possess higher accretion rates
and potentially be thermally unstable.  Past studies have found that
core galaxies show a wide range of nuclear radio and X-ray
luminosities (suggesting cyclic accretion episodes), while cusp
galaxies are confined below a threshold (e.g., \citealt{Bender+89,
  Pellegrini99, Capetti&Balmaverde05}), consistent with
thermally-stable, steady-state picture.

@@

We have calculated steady-state models for circumnuclear medium of
quiescent galaxies, assuming that gas is supplied entirely by stellar
wind mass loss and heated by shocked stellar winds, supernovae and
black hole feedback. We compute profile for a range of different black
hole masses, heating rates, and stellar density profiles and use these
profiles to calculate an $\Mdot$ onto each galaxy's SMBH, and get the
scaling of $\Mdot$ with $\Mbh$. We may then compare our results with
observed trends of Our main conclusions may be summarized as follows.

  \begin{enumerate}
  %Younger population=>higher accretion rate; generally higher eta and
  %lower vw except for very young stellar populations.
  \item We find that $\eddr \propto \Mbh^{}$ for
    $\Mbh\gsim4\times10^6$ and $\Mbh\lsim 2\times 10^8$, for galaxies
    following the average star formation histories measured in
    cosmological simulations \citep{MosterNaab+:2013a}. This is in
    tension observations of nuclear X-ray luminosity which suggest
    that $\eddr$ increases towards smaller $\Mbh$
    \citep{Miller+15}. However, it is important to note that the
    inflow rate on large scale (which we calculate) may differ from
    the actual accretion rate as outflows could occur on small
    scales. The outflow rate would depend on the angular momentum of
    the infalling gas and thus the angular momentum of stars in the
    nucleus. The in turn would vary systematically with $\Mbh$.
  \item We expect within scatter in nuclear x-ray luminosities at
    fixed $\Mbh$ from (1) stochastic variation in star formation
    history from galay to galaxy (2) Variations in small scale outflow
    rates due to variations between galactic nuclear angular momenta.
    These variations alone could explain much of the 2-4 orders of
    magnitude of scatter of nuclear x-ray luminosity at fixed $\Mbh$ 
    in the samples of \citet{Miller+15} and \citet{Pellegrini:2010a}.

    It is also possible that many of the galaxies in the
    \citet{Miller+15} are accreting in a non-steady fashion and this
    scatter arises from cyclic variation in accretion rate. In fact it
    that a population of cyclically accreting with $\Mbh\gsim 10^{8}
    \Msun$ coexists with a population of smaller, steadily accreting
    black holes (e.g. the upper limits in \citet{Miller+15}).  This
    calls into question the use of simple extrapolations of power-law
    fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$
    to constrain the occupation fraction of black holes in low mass
    galaxies (\citealt{Miller+15}).
  \item Low mass AGN have growth times comparable to the Hubble time
    \citet{Heckman+04}. We have shown that this would require accretion
    rates not consistent with steady-state thermally stable accretion
    of stellar wind material, and is driven by an external supply of gas.
  \item We compare the $\Mdot$ for each of our solution to the one
    calculated from the Bondi formula. We find that they agree to
    within a factor of order unity. This is because in our model the
    accretion rate is determined by the flow properties at the
    stagnation radius, $\rs$, which is within a factor of a few of the
    Bondi radius $\rb$. Thus, use of the Bondi formula is a
    good approximation.

>>>>

The source term in equation (\ref{eq:drhodt}),
\begin{align}
  q=\frac{\eta \rhostar}{\th},
\label{eq:q}
\end{align}
represents mass input from stellar winds, which we parameterize in
terms of the fraction $\eta$ of the stellar density $\rhostar$ being
recycled into gas on the Hubble time $\th = 1.4 \times 10^{10}$ yr.
To good approximation $\eta\simeq 0.02 (\tau_{\star}/t_h)^{-1.3}$ at
time $\tau_{\star}$ following an impulsive star burst (e.g.,
\citealt{Ciotti+91})\footnote{\citet{Ciotti+91} give the mass return
  rate from evolved stars as a function of B-band luminosity instead
  of volumetrically, but our expressions are equivalent.}, although
$\eta$ is significantly higher for continuous star formation histories
(bottom panel of Fig.~\ref{fig:vwSources}).

@@

Our analytic derviations neglect the effects of heat conduction, an assumption we now check.  The ratio of the magnitude of the conductive heating rate (eq.~[\ref{eq:qdotcond}]) to the external heating rate at the stagnation radius is given by
\begin{align}
  \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
w}^{2}/2}\right|_{r_{\rm s}} &\sim \frac{2t_{\rm h}\kappa_0
T|_{r_{\rm s}}^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}|_{r_{\rm s}}
\tilde{v}_{w}^{2}}
 \left(\frac{1}{1+\frac{\kappa_0 T^{7/2}|_{r_{\rm s}}}{5 \rs
    \phi \rho c_s^3}}\right)
\nonumber \\ &\sim {\rm min}
  \begin{cases}
  20 \eta_{0.02}^{-1}
M_{\bullet,8}^{-0.8} v_{500}^{6.8} &  \text{unsaturated (core)}\\
 20 \eta_{0.02}^{-1}
M_{\bullet,8}^{-0.5} v_{500}^{5.4} &  \text{unsaturated (cusp)}\\
  2 \phi & \text{saturated},
  \end{cases}
 \label{eq:conduction}
\end{align}
where the second equality makes use of equations (\ref{eq:Tanalytic}),
(\ref{eq:stag_simple}), and we have approximated $\nabla^{2} \sim
1/r_{\rm s}^{2}$, $\nabla \sim 1/r_{\rm s}$.  We have approximated the
stellar density profile as (eq.~[\ref{eq:rhostar}])
\begin{eqnarray}
  \rho_{\star}|_{r_{\rm s}} &\simeq& \frac{M_{\bullet}(2-\Gamma)}{4\pi r_{\rm soi}^{3}}\left(\frac{r_{\rm s}}{r_{\rm soi}}\right)^{-1-\Gamma} \nonumber \\
 &\approx& \begin{cases}
    6.1 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
    & \text{core} \\
    2.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
    \,{\rm g\,cm^{-3}}  & \text{cusp}, 
  \end{cases}
  \label{eq:rhostarrs}
\end{eqnarray}
where the stagnation radius is assume to reside well inside the Nuker
break radius and for clarity we have not distinguished between cusp
and core galaxies.  Equation (\ref{eq:conduction}) shows that even in
the case of saturated conduction, the neglect of heat conduction
results in at most an order unity correction for expected {\bf (AG:
  this sounds a bit too sharp perhaps replace with the word
  plausible. Perhaps we should also mention the phi=1 solutions have
  acausal conductivity (perhaps they are unphysical?).} values of
the saturation parameter $\phi < 0.1$, justifying its neglect in our
analysis.  Numerical experiments including conductivity confirm this
($\S\ref{sec:numerical}$).

@@

  \citet{EmsellemCappellari+:2007a} use two-dimensional kinematic data
  to measure the ratio of ordered to random motion in a sample of
  early type galaxies, which they quantify at each galactic radius $R$
  by the parameter
  \begin{align}
    \lambda_R \equiv \frac{\langle r|V|\rangle}{\langle R\sqrt{V^2+\sigma^2}\rangle} \underset{R \ll r_{\rm soi}}\sim \frac{V_{\phi}}{\sigma},
  \end{align}

  where $\sigma$ is the velocity dispersion and the brackets indicate
  a luminosity-weighted average.  The circularization radius of the
  accretion flow can be written in terms of $\lambda_R$ as

\begin{equation}
\frac{r_{\rm circ}}{r_{s}} \approx \frac{r_{s}}{r_{\rm soi}}\lambda_{R}^{2} \lesssim \lambda_{R}^{2},
\label{eq:rcirc}
\end{equation}

where we have used the definition $r_{\rm soi} \equiv
GM_{\bullet}/\sigma^{2}$ and in the second inequality have assumed
that $r_{\rm s} \lesssim r_{\rm soi}$, a condition which is satisfied
for the thermally-stable solutions of interest.

\citet{EmsellemCappellari+:2007a} (their Fig.~2) find that $\lambda_R$
is generally $< 0.1$ on radial scales $<$ 10 per cent of the galaxy
half-light radius and that $\lambda_R$ is with $R$ interior to this
point.  From equation (\ref{eq:rcirc}) we thus conclude that $r_{\rm
  circ} \lesssim 0.01r_{s}$, i.e.~that gas will circularize well
inside the inner sonic point of the flow (typically located at $r\lsim
0.1r_{\rm s}$; Fig.~\ref{fig:profiles}).  Angular momentum should only
become dynamically important for thermally stable flows in a region
that is causally disconnected from the outer part of the flow where
the mass accretion rate is determined.

@@

  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $\Gamma$ &  $r_{\rm
    s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm
          edd}}\frac{0.2}{\eta}\right)_{r_{s}}^{(c)}$} &
  {$\left(\frac{t_{\rm cool}}{t_{\rm
          ff}}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\

@@

...$^{\dagger}$ & ... & 0.8 & 100 & 0.29 & $ 1.5 \times 10^{ -4 }$ &
70 \\
...$^{\ddagger}$ & ... & 0.8 & 100 & 0.31 & $ 1.6 \times 10^{ -4 }$ & 73 \\

@@

$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 9.9 \times 10^{ -2 }$ & $ 8.2
\times 10^{ -6 }$ & 99 & Conv\\

@@

\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.
  $^{(b)}$ Break radius of stellar Nuker profile.  $^{(c)}$Accretion
  rate in Eddington units, normalized to a stellar mass input
  parameter $\eta = 0.2$.  $^{(d)}$Ratio of cooling timescale to
  free-fall timescale at stagnation radius.  Thermally unstable
  solutions are shown in bold text.  $\dagger$Calculated with
  radiative cooling included, assuming mass loss parameter $\eta =
  0.2$.  $\ddagger$Calculated with radiative cooling and conductivity
  included, assuming mass loss parameter $\eta = 0.2$ and conductivity
  saturatioon parameter $\phi=0.1$ (recall that we assume that the
  conductive heat flux saturates to $F_{\rm cond}=5\phi \rho c_s^3$). 
\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

Realistic variations (``burstiness") in the star formation history
will often result in lower heating rates.  Figure \ref{fig:NickPlot2}
shows the heating rate as a function of average black hole mass for
non-fiducial cases in which the current ($z = 0$) star formation is
suppressed by a factor $\zeta$ from its average $z = 0$ value, for a
characteristic timescale $t_{\rm scale}$ (for details, see Appendix
\ref{app:windheat}).  For $t_{\rm scale} \lesssim 10^{7}$ yr, we see
that $v_{\rm w}^{\star}$ is reduced by at most a factor of $\approx 2$
from its average value, even for huge drops in the star formation rate
($\zeta \sim 10^{-3}$).  However, burstiness in the star formation
history over longer timescales can suppress heating more
significantly.  When $t_{\rm scale} \gtrsim 10^8~{\rm yr}$, $v_{\rm
  w}^\star$ becomes very sensitive to $\zeta$: at $\zeta=0.1$, $v_{\rm
  w}^\star \approx 500~{\rm km~s}^{-1}$ in most galaxies, but for
smaller $\zeta$, $v_{\rm w}^\star \approx 200~{\rm km~s}^{-1}$ (an
exception to this is in galactic nuclei with $M_\bullet \gtrsim
5\times 10^8~M_\odot$, where heating is stabilized by SN Ia).  Our use
of average cosmic star formation histories is appropriate provided
local variations are either on short timescales ($t_{\rm scale}
\lesssim 10^7~{\rm yr}$), or limited in magnitude ($\zeta \gtrsim
0.1$).  If both of these conditions are violated, then the effective
heating rates for all but the most massive galaxies (where Ia
explosions dominate) will fall by a factor $\approx 5$ from our
fiducial volumetric averages, taken from \citet{MosterNaab+:2013a}.

@@

Figure \ref{fig:bh_growth} (top panel) shows that across all black
hole masses, Compton heating alone cannot prevent thermal
instabilities from developing in a steady-state accretion flow
($\dot{M}_{\rm C} > \dot{M}_{\rm TI}$).  Thus, if the stellar
population is sufficiently old (or the star formation sufficiently
intermittent) then nuclear gas could undergo cyclic oscillations of
thermal instability and high accretion rates, followed by quiescent
periods once gas has been consumed and/or AGN feedback becomes
effective.  Such cycles are proposed to occur on large scales and long
timescales in elliptical galaxies (\citealt{Ciotti+10}), an idea
supported, e.g. , by GALEX observations showing that a small fraction
of early-type galaxies in the local universe have undergone recent ($<
1-2$ Gyr old) star formation episodes (\citealt{Donas+07}).  If such
cyclic behavior also occurs on small, parsec scales (e.g.) then the
large scatter in the accretion rates and hence X-ray luminosities
shown in Fig \ref{fig:miller} could also be understood by the wide
range of gas masses experienced over the course of a cyclic episode
between instabilities and periodic nuclear outbursts
(e.g.~\citealt{Ciotti+10}).  In support of this possibility, we find
that core galaxies are more likely to possess higher accretion rates
and potentially be thermally unstable.  Past studies have found that
core galaxies show a wide range of nuclear radio and X-ray
luminosities (suggesting cyclic accretion episodes), while cusp
galaxies are confined below a threshold (e.g., \citealt{Bender+89,
  Pellegrini99, Capetti&Balmaverde05}), consistent with
thermally-stable, steady-state picture.

@@

We have calculated steady-state models for circumnuclear medium of
quiescent galaxies, assuming that gas is supplied entirely by stellar
wind mass loss and heated by shocked stellar winds, supernovae and
black hole feedback. We compute profiles for a range of different
black hole masses, heating rates, and stellar density profiles and use
these profiles to calculate an $\Mdot$ onto each galaxy's SMBH, and
get the scaling of $\Mdot$ with $\Mbh$. We may then compare our
results with observed trends of nuclear x-ray luminosity with galaxy
properties. Our main conclusions may be summarized as follows.

  \begin{enumerate}
  %Younger population=>higher accretion rate; generally higher eta and
  %lower vw except for very young stellar populations.
  \item We find that $\eddr \propto \Mbh^{}$ for
    $\Mbh\gsim4\times10^6$ and $\Mbh\lsim 2\times 10^8$, for galaxies
    following the average star formation histories measured in
    cosmological simulations \citep{MosterNaab+:2013a}. This is in
    tension observations of nuclear X-ray luminosity which suggest
    that $\eddr$ increases towards smaller $\Mbh$
    \citep{Miller+15}. However, it is important to note that the
    inflow rate on large scales (which we calculate) may differ from
    the actual accretion rate as outflows could occur on small
    scales. The outflow rate would depend on the angular momentum of
    the infalling gas and thus the angular momentum of stars in the
    nucleus. The in turn would vary systematically with $\Mbh$.
  \item We expect within scatter in nuclear x-ray luminosities at
    fixed $\Mbh$ from (1) stochastic variation in star formation
    history from galaxy to galaxy (2) Variations in small scale outflow
    rates due to variations between galactic nuclear angular momenta.
    These variations alone could explain much of the 2-4 orders of
    magnitude of scatter of nuclear x-ray luminosity at fixed $\Mbh$ 
    in the samples of \citet{Miller+15} and \citet{Pellegrini:2010a}.

    It is also possible that many of the galaxies in the
    \citet{Miller+15} are accreting in a non-steady fashion and this
    scatter arises from cyclic variation in accretion rate. In fact it
    that a population of cyclically accreting with $\Mbh\gsim 10^{8}
    \Msun$ coexists with a population of smaller, steadily accreting
    black holes (e.g. the upper limits in \citet{Miller+15}).  This
    calls into question the use of simple extrapolations of power-law
    fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$
    to constrain the occupation fraction of black holes in low mass
    galaxies (\citealt{Miller+15}).
  \item Low mass AGN have growth times comparable to the Hubble time
    (\citet{Heckman+04}). We have shown that this would require accretion
    rates not consistent with steady-state thermally stable accretion
    of stellar wind material, and is driven by an external supply of gas.
  \item We compare the $\Mdot$ for each of our solution to the one
    calculated from the Bondi formula. We find that they agree to
    within a factor of order unity. This is because in our model the
    accretion rate is determined by the flow properties at the
    stagnation radius, $\rs$, which is within a factor of a few of the
    Bondi radius $\rb$. Thus, use of the Bondi formula is a
    good approximation.
    \end{enumerate}
